### 2014-07-14 paper/introduction.tex
fitting

\changes{Recently, human-computer interaction researchers have begun to explore how to add interaction to 3D printed objects by creating appropriate structures inside those objects. They have introduced techniques such as printed light pipes~\cite{Willis-printedoptics} and printed hollow chambers for air pressure sensing~\cite{slyper}. These projects introduce point examples of particular techniques. In this paper we present a systematic design space of using 3D printed pipes and cavities, and introduce a design tool that enables makers to add interactivity to their models through internal pipes.}

>>>>

\changes{Recently, human-computer interaction researchers have begun to explore adding interaction to 3D printed objects by creating appropriate structures inside those objects. They have introduced techniques such as printed light pipes~\cite{Willis-printedoptics} and printed hollow chambers for air pressure sensing~\cite{Slyper-pressure}. These projects introduce point examples of particular techniques. In this paper we present a systematic design space of 3D printed pipes and cavities, and introduce a design tool enabling makers to add interactivity to their models using internal pipes.}
